Conditional selectivity for triplestores

### 2012-09-18 conditional/trunk/selectivity-basic.tex
distribution void additions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@384 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\subsection{Interesting distributions}

Uniform distributions have no impact on join order\todo{argue}.
\todo{Use parameterized stats for datatype properties?}

\subsection{Suggested additions to the VoID vocabulary}

Allthough a careful estimate of the selectivity in situations where we
have e.g. $\sel{O = ? | P = p \cap S = ?}$ would require a two
dimensional distribution function, the most significant impacts on
join order is when the distribution is highly skewed\todo{argue}. A
hint to the optimizer in such cases could be achieved by the addition
of properties like \rdfterm{void:mostFrequentObjects},
\rdfterm{void:mostFrequentSubjects},
\rdfterm{void:leastFrequentObjects} and 
\rdfterm{void:leastFrequentSubjects} to property
partitions.\todo{mention the dc:language case in Sublima?}
